TBD

### 2021-03-05 outputs/paper/paper.Rmd
educational level by PID

---
title: "TBD"
subtitle: "TBD"
author: "TBD"
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

```{r loaddata, echo=FALSE}
library(here) # locate the file path

@@

# EDA

## treat distribution 
```{r treat, fig.cap = "Employee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}

@@

## education level distribution by PID

## sexim by education level 
```{r sexim, fig.cap = "sexim by education level",echo=FALSE, fig.width=5, fig.height=4}

@@

## internet usage by meta.os
```{r internet, fig.cap = "internet usage by os",echo=FALSE, fig.width=5, fig.height=4}

@@

## post favor by treat

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

Weaknesses and next steps should also be included.

@@

# Appendix {-}

# Additional details

>>>>

---
title: "TBD"
subtitle: "TBD"
author: "Yingying Zhou, Yang Wu, Xinyi Xu, Hong Pan"
thanks: "Code and data are available at: https://github.com/yangg1224/Political_Deepfake_Videos.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
  toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE,echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

```{r loaddata, echo=FALSE, warning=FALSE, message=FALSE}
library(here) # locate the file path

@@

## EDA

### treat distribution 
```{r treat, fig.cap = "Employee numbers distribution",echo=FALSE, fig.width=10, fig.height=4}

@@

### education level distribution by PID 
```{r educationPID, fig.cap = "Educational level by PID",echo=FALSE, fig.width=10, fig.height=7}
edu <- 
  EDA%>%
  ggplot(aes(x = EDA$educ,fill=EDA$PID, )) +
  geom_bar(position="dodge") +
  labs(title = "Citizens with a high school degree or above are more likely to suppprt democratic and republican party",x= "Educational Level", y="Count")+
  scale_fill_manual(name = "Political Parties",values = c("#DB7558", "#FFCF57","#8FCDD4"))

edu
```

### sexim by education level 
```{r sexim, fig.cap = "sexim by education level",echo=FALSE, fig.width=5, fig.height=4}

@@

### internet usage by meta.os
```{r internet, fig.cap = "internet usage by os",echo=FALSE, fig.width=5, fig.height=4}

@@

### post favor by treat

@@

@@

@@

# Appendix
